On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-11-23 paper/paper.tex
Motivation: describe the current state of EDSLs wrt pattern matching and how this improves on it

% \newpage
Haskell EDSLs that support powerful language features like pattern matching
allow these advantages to be brought to problem domains where it is currently
either difficult or impossible to use a language that has these benefits.

>>>>

% \newpage
Haskell EDSLs that support powerful language features like pattern matching
allow these advantages to be brought to problem domains where it is currently
either difficult or impossible to use a language that has these benefits.
However, there is no support for capturing pattern matching builtin to the Haskell
language itself. As a result, EDLs which capture pattern matching must do so
via a plugin in a Haskell compiler such as GHC. For each such EDSL, this mechanism
has needed to be reimplemented each time. In this paper, we descibe a \textit{reusable}
framework for capturing pattern matching, as well as lambdas and tail recursion.
